Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-21 automatica/paper.tex
remove noise from diagram

   \& complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
   }

@@

   \& complexnode/.pic={ 
     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
     \coordinate (switch1) at ([xshift=-1cm]adc.center);
     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{x}_k$};       
     \coordinate (ykeast) at ([xshift=1.9cm]q1);
     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]q1);
   } 
   \& \coordinate (aux1);
   \& \\
  };

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (r) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (yksouth)
   (yksouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system 
 \label{fig:digitalsystem}}
\end{figure*}

>>>>

   \& complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
   %  \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
     \node[fill=gray!20] (zoh) at ([xshift=.0cm]dac.center) {\sc ZOH};
   }

@@

   \& complexnode/.pic={ 
     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
     \coordinate (switch1) at ([xshift=-1cm]adc.center);
     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
   %  \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]switch2)  {$\vec{x}_k$};       
     \coordinate (ykeast) at ([xshift=2.9cm]switch2);
     \coordinate (yksouth) at ([xshift=2.9cm,yshift=-3.5cm]switch2);
   } 
   \& \coordinate (aux1);
   \& \\
  };

%  \path[->] (v1) edge (q1.south);
%  \path[->] (v2) edge (q2.south);
  \path[->] (r) edge (circle.west);
  \path[->] (circle.east) edge (zoh.west);
%  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (switch1.west)
   (switch2) edge (ykeast);
  \path
 %  (q1.east) edge (ykeast)
   (ykeast) edge (yksouth)
   (yksouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system 
 \label{fig:digitalsystem}}
\end{figure*}
